---
title: "create_data"
output: html_document
---

```{r setup, include=FALSE}
library(glptools)
glp_load_packages()

library(survey)
```

Vehicle Access

Current output is vehicle access at the county and tract level
Data on means of transportation to work are available by race, but not vehice access. Could use microdata to disaggregate. 
```{r cars}
vehicle_vars_1yr <- build_census_var_df("acs1", "B08201", 
                                        additional_filters = "^Estimate!!Total(!!No vehicle available)?$")
vehicle_vars_5yr <- build_census_var_df("acs5", "B08201", 
                                        additional_filters = "^Estimate!!Total(!!No vehicle available)?$")

vehicle_county <- get_census(vehicle_vars_1yr, geog = "FIPS")
vehicle_map    <- get_census(vehicle_vars_5yr, geog = "tract")

vehicle_access_county <- vehicle_county %>%
  mutate(vehicle = if_else(str_detect(label, "No vehicle available"), F, T)) %>%
  process_census(cat_var = "vehicle", output_name = "vehicle_access")

vehicle_map %<>% 
  mutate(vehicle = if_else(str_detect(label, "No vehicle available"), F, T)) %>%
  process_census(cat_var = "vehicle", output_name = "vehicle_access")

process_map(vehicle_map, vehicle_access, return_name = "vehicle_access", pop = vehicle_access_pop) %>% list2env(.GlobalEnv)
  
save(vehicle_access_county, vehicle_access_tract, vehicle_access_nh, vehicle_access_muw, 
     file = "output_data/vehicle_access.RData")
```

Food Security

Food security data comes from the December supplement. 
Because the number of unique housholds included in each December supplement is very small, sampling error is large. I use a "rolling survey" function to pool years of data together for estimates, similar to ACS 3-year or 5-year data.
```{r}
cps_micro <- feather::read_feather("../../glpdata/data-raw/microdata/cps_micro.feather")

# Create food security category variable and food security dummy variable.
cps_micro %<>%
  mutate(
    food_security_cat = case_when(
      FSSTATUS == 1 ~ "food_secure",
      FSSTATUS == 2 ~ "low_food_secure",
      FSSTATUS == 3 ~ "very_low_food_secure",
      TRUE          ~ NA_character_),
    food_insecure = case_when(
      FSSTATUS == 1 ~ 0,
      FSSTATUS %in% 2:3 ~ 1,
      TRUE ~ NA_real_))

# Filter to December supplement and remove households which appear in the survey twice.
cps_micro %<>% 
  filter(MONTH == 12) %>%
  filter(!duplicated(CPSID))

rolling_svy <- function(df, rm, geog) {
  
  # Calculate years for output based on the rolling mean (i.e. 2005:2017 or 2006:2016)
  years_original <- 2004:2018
  years <- rollmeanr(years_original, rm)
  years <- years[!is.na(years)]
  
  # FIPS codes from the entire MSA are included in the data.
  # If using FIPS, remove FIPS codes outside the core counties.
  if (geog == "FIPS") df %<>% pull_peers(geog = "FIPS")
  
  # For y in years, filter to rm years centered around y and run a survey
  for (y in years) {
    
    these_years = (y-floor(rm/2)):(y+floor(rm/2))
    
    temp <- df %>%
      filter(year %in% these_years)
    
    svy_obj <- svydesign(ids = ~1, weights = ~HWTFINL, data = temp)
    
    svy_df <- svyby(~food_insecure, as.formula(paste0("~", geog)), design = svy_obj, svymean, na.rm = TRUE)
    
    svy_df$year <- y
    
    output <- assign_row_join(output, svy_df)
  }
  
  output %<>% select(any_of(c("MSA", "FIPS", "year", "food_insecure", "se")))
}

food_security_1yr <- rolling_svy(cps_micro, 1, "MSA")
food_security_3yr <- rolling_svy(cps_micro, 3, "MSA")
food_security_5yr <- rolling_svy(cps_micro, 5, "MSA")

# Evaluate se as a percent out of 100 and as a margin or error around food insecurity
mean(food_security_1yr$se)
mean(food_security_3yr$se)
mean(food_security_5yr$se)

mean(food_security_1yr$se / food_security_1yr$food_insecure * 100, na.rm = T)
mean(food_security_3yr$se / food_security_3yr$food_insecure * 100, na.rm = T)
mean(food_security_5yr$se / food_security_5yr$food_insecure * 100, na.rm = T)

save(food_security_1yr, food_security_3yr, food_security_5yr,
     file = "output_data/food_security.RData")
```
